Cross-Loop Optimization of Arithmetic Intensity for Finite Element Local Assembly

### 2014-09-02 TACO-paper-v2/coffee.tex
minor fixes, add TODOs

\item The various sub-expressions in $\beta$ only depend on (i.e. iterate along) a subset of the enclosing loops. In addition, some of these sub-expressions might reduce to the same values as iterating along certain iteration spaces. This code structure motivated the generalized loop-invariant code motion technique. The intuition is that whenever sub-expressions invariant with respect to different sets of affine loops can be identified, the question of whether, where and how to hoist them, while minimizing redundant computation, arises.  

@@

\item \textbf{Multi-loop vectorization.} Compiler auto-vectorization has become effective for a variety of codes. Nevertheless, multi-loop vectorization, which involves loading and storing data along a subset of the loops characterizing the iteration space (rather than just along the innermost loop), is not supported by available general-purpose and polyhedral compilers to the best of our knowledge. However, the outer-product vectorization technique presented in this paper shows that two-loop vectorization can outperform standard auto-vectorization; more importantly, we expect the performance gain to scale with the number of vectorized loops and the vector length (as proved by the Xeon Phi results). Despite being not straightforward to automate multi-loop vectorization in a general-purpose compiler, especially if stencils are present, we believe that in specific domains this could be more easily achieved. The intuition is to map the memory access pattern on vector registers, and then relying on in-register shuffling to minimize the traffic between memory and processor.

>>>>

\item The various sub-expressions in $\beta$ only depend on (i.e. iterate along) a subset of the enclosing loops. In addition, some of these sub-expressions might reduce to the same values as iterating along certain iteration spaces. This code structure motivated the generalized loop-invariant code motion technique. The intuition is that whenever sub-expressions invariant with respect to different sets of affine loops can be identified, the question of whether, where and how to hoist them, while minimizing redundant computation, arises.  TODO: hoisting requires extra memory, so what should one do?

@@

\item \textbf{Multi-loop vectorization.} Compiler auto-vectorization has become effective for a variety of codes. Nevertheless, multi-loop vectorization, which involves loading and storing data along a subset of the loops characterizing the iteration space (rather than just along the innermost loop), is not supported by available general-purpose and polyhedral compilers to the best of our knowledge. The outer-product vectorization technique presented in this paper shows that two-loop vectorization can outperform standard auto-vectorization; more importantly, we expect the performance gain to scale with the number of vectorized loops and the vector length (as proved by the Xeon Phi results). Despite being not straightforward to automate multi-loop vectorization in a general-purpose compiler, especially if stencils are present, we believe that in specific domains this could be more easily achieved. The intuition is to map the memory access pattern on vector registers, and then relying on in-register shuffling to minimize the traffic between memory and processor.
